---
title: "R4DS-Chapt1"
author: "Sarena"
format:
  html:
    toc: true
editor: visual
---

https://r4ds.had.co.nz/introduction.html

## What I think I will learn

-   how to use ggplot to make a chart

## load packages

to insert a code chunk hit control alt i

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
```

## definitions of chapt1

-   tidy: storing your data in a consistent form so you can focus on other parts of the data.

-   transform: narrow down on interests and new variables from existing variables

-   model: used to visualize and find answers to questions

## lack of programming experience help

-   adjacent read to help is hands on programming with r by Garrett

## need the following to ru code for this book

-   R
-   RStudio
-   tidyverse
-   other helpful packages

## running R code

```{r}
1 + 2 
```

## random notes

-   sum() or mean()
-   packages should be loaded at top of script so if updates are needed it can be done.
-   include data in a question with dput()

## make your code readable

-   use spaces
-   concise and informative variable names
-   use comments
-   delete unneeded junk from code
-   solve problems before they occur
